---
title: "CNCDriver Tutorial"
author:
- name: Eric Minwei Liu
  affiliation: Weill Cornell Medicine, New York, NY, USA
- name: Ekta Khurana
  affiliation: Weill Cornell Medicine, New York, NY, USA
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc: yes
    toc_float: no
  BiocStyle::pdf_document: default
vignette: |
  %\VignetteIndexEntry{CNCDriver Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r knitrSetup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"', fig.align="center", fig.width=12, fig.height=12, tidy=TRUE)
```

```{r style, include=FALSE, echo=FALSE, results='asis'}
BiocStyle::markdown()
```

# Overview

The **CNCDriver** combined mutation recurrence and functional impact to identify
coding and non-coding cancer drivers

# Basics
## Installation

```{r installCNCDriver, eval=FALSE}
library(remotes)
install_github(repo="khuranalab/CNCDriver", ref="master", build_vignette=TRUE)
```

## Getting Started

Load **CNCDriver** package: 

```{r loadLibrary, message=FALSE, warning=FALSE}
library(CNCDriver)
```

A list of all accessible vignettes and methods is available with the following command: 

```{r searchHelp, eval=FALSE, tidy=FALSE}
help.search("CNCDriver")
```

For help on any **CNCDriver** package functions, use one of the following command formats:

```{r showHelp, eval=FALSE, tidy=FALSE}

help(getCDSPvalue)
?getCDSPvalue
```

## Load FunSeq2 annotations of WGS SNV mutation calls in LGG. 

Load pre-parsed FunSeq2 annotations of WGS SNV mutation calls in BRCA.
The whole genome sequencing SNV mutation calls in BRCA are from Fredriksson et al. Nature Genetics 2015. WGS SNV data is available at 

```{r netboxrExampleNetwork}
# Load pre-parsed FunSeq2 annotations for SNV mutation calls in LGG.
data("reducedFunseqOutputCDS")
data("reducedFunseqOutputNCDS")
```





# References

* Eric Minwei Liu, Alexander Martinez Fundichely, Bianca Jay Diaz, Boaz Aronson, Tawny Cuykendall, Matthew MacKay, Priyanka Dhingra, Elissa WP Wong, Ping Chi, Effie Apostolou, Neville E Sanjana, Ekta Khurana “Identification of Cancer Drivers at CTCF Insulators in 1,962 Whole Genomes”, Cell Systems, 8,4460455. e8 (2019)

# Session Information

```{r sessionInfo}
sessionInfo()
```


